---
title: "R markdown in class memo"
author: "Alvina Chan"
date: "2023-09-21"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## This is my level 1 heading (2 hashes)

### This is my level 2 heading (3 hashes)

#### This is my level 3 heading (4 hashes)

##### This is my leve 4 heading (5 hashes)

This is my main text. POLI3148 is the course

# **Add code to your document (put a slash then there will be options then select r code chunk)**

```{r}
log(50)
```

```{r}
1+1

```

# Output Figures

```{r}
plot(1:10, 1:10)
```

# Display data (cars data as test)

```{r}
cars
```

# Use Tools, Global options then click R Markdown for preview in pane / evaluate by project

# Inline R code

Scientific research shows that 12223+12111 =

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

install.packages("tinytex")

```{r}
#install.packages("tinytex")
#tinytext::instal>tinytex()
#```install.packages("tinytex")
#tinytex::install_tinytex()


# ```{r}
#install.packages("tinytex")
#tinytex::install_tinytex()



```
